---
title: "Complex detection manuscript figures"
author: "Leo Dahl"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
    toc: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(stringsAsFactors = F)
```

Description
===========

> Making manuscript figures for GPCR-RAMP complex detection. Some figures require multiple plots to be combined in specific layouts, these figures are made in this script. 

Packages and data
=================

```{r packages, message=F, warning=F}

rm(list = ls())

library(tidyverse)
library(magrittr)
library(patchwork)
library(data.table)
library(grid)
library(ComplexHeatmap)
library(circlize)
library(ggbeeswarm)
library(readxl)
library(openxlsx)
library(RColorBrewer)
library(DescTools)
library(ggplotify)
library(ggh4x)
library(ComplexUpset)
library(ggdendro)
library(ggvenn)
library(limma)

source("misc_functions_cxdet.R")

```

```{r data}

# Load app data and reshape to work with the code in this script
# List containing the long data from the assays and the endogenous assay data
appdat <- readRDS("gpcr_cxdet_data.rds")

datlist <- sapply(c("r", "z", "rz"), function(x) {
  # Data to base the list on
  d <- appdat

  # Names of value columns to keep or skip
  val_skip <- paste0("value_", setdiff(c("r", "z", "rz"), x))
  val_keep <- paste0("value_", x)
  
  d$long_dat_all <- d$long_dat_all %>% select(-!!val_skip) %>% rename("value" = !!val_keep)
  
  return(d[c("prot", "long_dat_all")])
}, simplify = F)

rdat <- datlist$r
zdat <- datlist$z
rzdat <- datlist$rz

# For the expression check use all samples, for the rest exclude gpcr.p11 plate samples as they have different interactors
expr_dat <- rdat

rdat$long_dat_all <- rdat$long_dat_all %>% filter(sample_type != "gpcr.p11")
zdat$long_dat_all <- zdat$long_dat_all %>% filter(sample_type != "gpcr.p11")
rzdat$long_dat_all <- rzdat$long_dat_all %>% filter(sample_type != "gpcr.p11")

# Endogenous interaction data
valid_dat <- appdat$valid_dat

rm(datlist, appdat)

out_dir <- "results/"

```

Plots
=====

RAMP expression
---------------

Fig S4A

```{r}

# RAMP expression (log2 data), capture either HA or one of the RAMPs, detect with OLLAS

# Get p-values, y positions and labels for each interactor with each capture method
# Same method as in Ab validation (anova + dunnett multiple comaprison test)
ramp_expr_test <- expr_dat$long_dat_all %>%
  filter(gene_name %in% c(paste0("RAMP", 1:3), "M anti-HA"),
         detection_ab == "OLLAS",
         interactor %in% c(paste0("RAMP", 1:3), "mock")) %>%
  select(gene_name, interactor, value) %>%
  mutate(gene_name = str_remove(gene_name, "M anti-")) %>%
  group_by(gene_name) %>%
  nest() %>%
  mutate(p = map(data, ~ {
    # Anova
    ap <- summary(aov(value ~ interactor, data = .x))[[1]] %>% as.data.frame() %>% mutate(Capture = gene_name)
    
    # Dunnett's multiple comparison test
    dp <- DunnettTest(x = .x$value, g = as.factor(.x$interactor), control = "mock")$mock %>%
      as.data.frame() %>% rownames_to_column("interactor") %>% mutate(interactor = str_remove(interactor, "-mock")) %>%
      mutate(capture = gene_name) %>% left_join(count(.x, interactor), by = "interactor")
    
    # y positions of labels
    p_ypos <- .x %>% filter(interactor != "mock") %>% group_by(interactor) %>%
      summarise(ypos = max(value, na.rm = T) + 0.3 * diff(range(value, na.rm = T))) %>% ungroup() %>%
      mutate("gene_name" = gene_name,
             "pval" = case_when(ap[1, 5] < 0.05 ~ dp[match(interactor, dp$interactor), "pval", drop = T],
                                T ~ 1),
             "pstar" = p_to_star(pval))
    
    return(list("anova" = ap, "dunnett" = dp, "plot_p" = p_ypos))
    
  })) %>%
  pull(p)

ramp_expr_anova_p <- lapply(ramp_expr_test, function(x) {as.data.frame(x$anova)[1, ]}) %>% data.table::rbindlist()
ramp_expr_dunnett_p <- lapply(ramp_expr_test, function(x) {as.data.frame(x$dunnett)}) %>% data.table::rbindlist()

# For table
ramp_expr_p <- lapply(ramp_expr_test, function(x) x$plot_p) %>% data.table::rbindlist()

# Plot with p-value labels
ramp_expr_plot <- expr_dat$long_dat_all %>%
  filter(gene_name %in% c(paste0("RAMP", 1:3), "M anti-HA"),
         detection_ab == "OLLAS",
         interactor %in% c(paste0("RAMP", 1:3), "mock")) %>% # sample_type != "gpcr.p11"
  select(gene_name, interactor, value) %>%
  mutate(gene_name = str_remove(gene_name, "M anti-")) %>%
  ggplot() +
  geom_violin(aes(x = interactor, y = log2(value), fill = interactor), show.legend = F) +
  geom_text(aes(x = interactor, y = log2(ypos), label = pstar), ramp_expr_p, size = 6) +
  stat_summary(aes(x = interactor, y = log2(value)), fun = mean, fun.min = mean, fun.max = mean,
               geom = "errorbar", colour = "black", width = 0.25) +
  geom_hline(yintercept = -Inf, linewidth = 2) + geom_vline(xintercept = -Inf, linewidth = 2) +
  scale_fill_manual(values = c("RAMP1" = "#BFEFFF", "RAMP2" = "#B1E063", "RAMP3" = "#EEAD0E", "mock" = "white")) +
  scale_x_discrete(labels = paste0("any.", c("mock", "RAMP1", "RAMP2", "RAMP3"))) +
  labs(x = NULL, y = "log2(MFI)", title = "Capture target") +
  facet_wrap(~ gene_name, nrow = 1) +
  theme_classic() +
  theme(axis.line = element_blank(),
        plot.title = element_text(size = 14, hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = 14),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 14),
        strip.text = element_text(size = 14),
        strip.background = element_rect(size = 2),
        axis.ticks = element_line(size = 1))

```

```{r}
# Remove now unnecessary data
rm(expr_dat)
ramp_expr_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_ramp_expr.pdf")
ggsave(filename = ramp_expr_name, plot = ramp_expr_plot, width = 11, height = 4.2)
```


Complex detection, epitope capture
----------------------------------

```{r}
# GPCRs to use
gpcrs <- sort(unique(rzdat$long_dat_all$gpcr))
gpcrs <- gpcrs[!gpcrs %in% c("empty", "mock")]

# Perform complex detection and make sensitivity/specificity plots
cxdet_prep_list <- cxdet_prep(gpcrs, rzdat)
cxdet_cd_sep <- gpcrramp_sensspec(rzdat$long_dat_all, gpcrs,
                                  cxdet_prep_list$expr_list, cxdet_prep_list$int_exp,
                                  mk_plts = T)

```


Cutoff table
------------

Table S5

```{r}
co_tbl <- cxdet_cd_sep$cutoffs %>%
  rename(Interaction = which_ramp,
         Capture = capt, Detection = det,
         Threshold = cutoff,
         Sensitivity = sens, Specificity = spec)

write_csv(co_tbl, paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_epitope_capt_thresholds.csv"))
```

HPA capture summary
-------------------

```{r}

# Interactions
cxdet_dens_res <- cxdet_dens(rzdat$long_dat_all, rzdat$prot, var_measure = mad, n_var = 6)

# Expected interactions
abs <- cxdet_dens_res$interactions$gene_name_id
int_exp <- data.frame("gene_name_id" = abs,
                      "gene_name" = rzdat$prot[match(abs, rzdat$prot$gene_name_id), "gene_name"],
                      "antibody" = rzdat$prot[match(abs, rzdat$prot$gene_name_id), "antibody"]) %>%
  unite("gene_name_ab", gene_name, antibody, remove = F) %>%
  # Deal with multi-target Abs
  mutate(gene_name_match = gene_name) %>%
  separate_rows(gene_name_match, sep = ";") %>%
  left_join(., cxdet_prep_list$int_exp %>% rename("gene_name_match" = "which_gpcr"), by = "gene_name_match") %>%
  filter(!is.na(which_ramp)) %>% select(gene_name_ab, gene_name, which_ramp, int_exp) %>% distinct() %>%
  pivot_wider(id_cols = c(gene_name_ab, gene_name), names_from = which_ramp, values_from = int_exp)


```

Table S6

```{r}
# Table of interactions + thresholds
cxdet_prot_tbl <- cxdet_dens_res$interactions %>% select(-c(gene_name_id, data, plt)) %>%
  separate(gene_name_ab, c("GPCR", "Antibody"), sep = "_") %>% rename(Threshold = cutoff) %>%
  mutate(across(where(is.logical), function(x) ifelse(x, "Pass", "Fail"))) %>%
  # Add RRIDs
  left_join(rzdat$prot %>% select(antibody, rrid), by = c("Antibody" = "antibody")) %>%
  rename("RRID" = "rrid") %>% relocate(RRID, .before = 3)

cxdet_prot_tbl_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_cxdet_prot_tbl.xlsx")
write.xlsx(cxdet_prot_tbl, cxdet_prot_tbl_name, asTable = F, overwrite = T)
```


Epitope and HPA capture together
--------------------------------

Sensitivity/Specificity and barplots for epitope and HPA capture. Figure 2 (A and B)

```{r}
# Horizontal barplots for epitope capture
cxdet_bar_horiz <- cxdet_cd_sep$interactions %>%
  group_by(capt, which_ramp) %>%
  count(pass) %>%
  ungroup() %>%
  filter(!is.na(pass)) %>%
  mutate(pass = factor(as.character(pass), levels = c("0", "1"))) %>%
  mutate(capt = factor(capt, levels = sort(unique(capt), decreasing = T))) %>%
  ggplot(aes(x = n, y = capt, fill = pass)) +
  geom_bar(stat = "identity", show.legend = F) +
  labs(x = "Number of GPCRs", y = NULL) +
  scale_fill_brewer(palette = "Set2", direction = -1) +
  scale_x_continuous(position = "top") +
  facet_grid2(rows = vars(which_ramp), drop = T, scales = "free", independent = T) +
  theme_minimal() +
  theme(strip.text = element_blank(),
        axis.text = element_text(size = 10, colour = "black"),
        axis.title = element_text(size = 12, colour = "black"))

# Data for barplot of interactions
cxdet_dens_bardat <- cxdet_dens_res$interactions %>%
  select(gene_name_id, contains("RAMP")) %>%
  pivot_longer(cols = -gene_name_id, names_to = "ramp", values_to = "pass") %>%
  filter(!is.na(pass)) %>%
  count(ramp, pass)

# Include total in y-axis ticks
ab_tot <- cxdet_dens_bardat %>% group_by(ramp) %>% summarise(s = sum(n)) %>% pull(s) %>% max()
yticks <- seq(0, ab_tot, by = 50)
if (!ab_tot %in% yticks) {yticks <- append(yticks, ab_tot)}
cxdet_dens_barplt <- ggplot(cxdet_dens_bardat, aes(x = ramp, y = n, fill = pass)) +
  geom_bar(stat = "identity", show.legend = F) +
  scale_fill_brewer(palette = "Set2", direction = -1) +
  scale_y_continuous(breaks = yticks) +
  labs(x = NULL, y = "Count") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5, size = 14),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 14))

# Horizontal barplots for HPA capture
cxdet_dens_bar_horiz <- cxdet_dens_bardat %>%
  mutate(ramp = factor(ramp, levels = sort(unique(ramp), decreasing = T))) %>%
  ggplot(aes(x = n, y = ramp, fill = pass)) +
  geom_bar(stat = "identity", show.legend = T) +
  scale_fill_brewer(palette = "Set2", direction = -1, labels = c("False", "True")) +
  scale_x_continuous(breaks = yticks, position = "top") +
  labs(x = "Number of anti-GPCR antibodies", y = NULL, fill = "Complex detected") +
  theme_minimal() +
  theme(axis.text = element_text(size = 10, colour = "black"),
        axis.title = element_text(size = 12, colour = "black"))

# Plot-side annotation
text_topright <- ggplot(data.frame(a = "Epitope\nantibody capture", x = 1, y = 1)) +
  geom_text(aes(x = x, y = y, label = a), angle = -90, size = 4) +
  geom_vline(xintercept = 0.9, linewidth = 0.8) +
  xlim(0.9, 1.1) +
  theme_void() +
  coord_cartesian(clip = "off")

text_botright <- ggplot(data.frame(a = "Native GPCR\nantibody capture", x = 1, y = 1)) +
  geom_text(aes(x = x, y = y, label = a), angle = -90, size = 4) +
  theme_void() +
  coord_cartesian(clip = "off")

dsgn <- "
AAAABBBD
AAAABBBD
AAAABBBD
AAAACCCE
"
cxdet_both_plt <-
  (cxdet_cd_sep$plots + labs(y = "Probability", tag = "A") +
     theme(axis.text = element_text(size = 12, colour = "black"),
           axis.title = element_text(size = 12, colour = "black"),
           strip.text = element_text(size = 11))) +
  (cxdet_bar_horiz + labs(tag = "B")) +
  cxdet_dens_bar_horiz +
  text_topright + text_botright +
  plot_layout(design = dsgn) &
  # Common layout parameters
  theme(legend.position = "bottom",
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 12),
        plot.tag = element_text(size = 18))

```

```{r}
cxdet_both_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_cxdet_fig2n3.pdf")
ggsave(filename = cxdet_both_name, plot = cxdet_both_plt, width = 7.25, height = 7.5)
```

Heatmaps for the different capture schemes. Figure S5

```{r}

# Make epitope capture heatmap split in two
splits <- split(gpcrs,
                ceiling(1:length(gpcrs)/ceiling(length(gpcrs)/2)))

epi_hm_gg <- lapply(splits, function(x) {
  grid.grabExpr(draw(pass_hm(cxdet_cd_sep$interactions %>% filter(which_gpcr %in% x), draw_hm = F)$heatmap))
})

cxdet_epi_hm <- wrap_plots(epi_hm_gg, nrow = 1, widths = c(1, 1))

# Heatmap of protein capture interactions
splits <- split(1:nrow(cxdet_dens_res$interactions),
                ceiling(1:nrow(cxdet_dens_res$interactions)/ceiling(nrow(cxdet_dens_res$interactions)/2)))

spl_hm <- lapply(splits, function(x) {
  dens_pass_hm(cxdet_dens_res$interactions[x, ], int_exp, col_name_bot = F)
})

hm_gg <- sapply(names(spl_hm), function(x) {
  if (x == names(spl_hm)[length(spl_hm)]) {
    # Add legend to final plot
    grid.grabExpr(draw(spl_hm[[x]]$heatmap, annotation_legend_list = spl_hm[[x]]$legend))
  } else {
    grid.grabExpr(draw(spl_hm[[x]]$heatmap))
  }
}, simplify = F)

cxdet_dens_hm <- wrap_plots(hm_gg, nrow = 1, widths = c(1, 2.4))

# Combine epitope and HPA capture heatmaps
pass_hm_both <- wrap_plots(list(cxdet_epi_hm, cxdet_dens_hm), widths = c(1, 0.98))

```


```{r}
hm_both_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_pass_hm_both.pdf")
ggsave(filename = hm_both_name, plot = pass_hm_both, width = 7, height = 8)
```

Summarising table
-----------------

Table S7

```{r}
# Make summary tables containing results from both epitope and protein capture
# Categorised evidence of interaction, number of passing schemes, percent of passing schemes
# Also add header rows for excel
sum_tbl <- rbind(
  cxdet_cd_sep$interaction_evidence %>% select(contains("which"), int_evid) %>% mutate(capt = "Epitope"),
  cxdet_dens_res$interaction_evidence %>% select(contains("which"), int_evid) %>% mutate(capt = "Protein"),
  cxdet_cd_sep$interactions %>% select(contains("which"), int_exp) %>% rename(int_evid = int_exp) %>% mutate(capt = "Literature") %>% distinct()
) %>%
  pivot_wider(id_cols = which_gpcr, names_from = c(which_ramp, capt), values_from = int_evid) %>%
  relocate(which_gpcr, contains("RAMP1"), contains("RAMP2"), contains("RAMP3"))
sum_tbl <- rbind(
  data.frame(c("", "GPCR"), str_split(colnames(sum_tbl)[-1], "_")) %>% setNames(colnames(sum_tbl)),
  sum_tbl
)

sum_tbl_n <- rbind(
  cxdet_cd_sep$interaction_n %>% mutate(capt = "Epitope"),
  cxdet_dens_res$interaction_n %>% mutate(capt = "Protein")
) %>%
  pivot_wider(id_cols = which_gpcr, names_from = c(which_ramp, capt), values_from = n_pass) %>%
  relocate(which_gpcr, contains("RAMP1"), contains("RAMP2"), contains("RAMP3")) %>%
  ungroup()
sum_tbl_n <- rbind(
  data.frame(c("", "GPCR"), str_split(colnames(sum_tbl_n)[-1], "_")) %>% setNames(colnames(sum_tbl_n)),
  sum_tbl_n
)

sum_tbl_fraction <- rbind(
  cxdet_cd_sep$interaction_evidence %>% select(contains("which"), fraction_pass) %>% mutate(capt = "Epitope"),
  cxdet_dens_res$interaction_evidence %>% select(contains("which"), fraction_pass) %>% mutate(capt = "Protein")
) %>%
  pivot_wider(id_cols = which_gpcr, names_from = c(which_ramp, capt), values_from = fraction_pass) %>%
  relocate(which_gpcr, contains("RAMP1"), contains("RAMP2"), contains("RAMP3"))
sum_tbl_fraction <- rbind(
  data.frame(c("", "GPCR"), str_split(colnames(sum_tbl_fraction)[-1], "_")) %>% setNames(colnames(sum_tbl_fraction)),
  sum_tbl_fraction
)
```

```{r}
# Save summary tables as one excel file
sum_tbl_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_summary_tbl.xlsx")
wb <- createWorkbook()
# Loop over tables to add to sheet while adding extra formatting
for (i in 1:3) {
  addWorksheet(wb, switch(i,
                          "1" = "Evidence of interaction",
                          "2" = "Number of passing schemes",
                          "3" = "Fraction of passing schemes"))
  tbl_in <- switch(i, "1" = sum_tbl, "2" = sum_tbl_n, "3" = sum_tbl_fraction)
  writeData(wb, i, tbl_in, colNames = F)
  addStyle(wb, i, createStyle(textDecoration = "bold", border = "TopBottomLeftRight"), rep(2, ncol(tbl_in)), 1:ncol(tbl_in))
  addStyle(wb, i, createStyle(halign = "center", textDecoration = "bold",  border = "TopBottomLeftRight"),
           rep(1, ncol(tbl_in)), 1:ncol(tbl_in))
  mergeCells(wb, i, str_which(tbl_in[1, ], "RAMP1"), rep(1, length(str_which(tbl_in[1, ], "RAMP1"))))
  mergeCells(wb, i, str_which(tbl_in[1, ], "RAMP2"), rep(1, length(str_which(tbl_in[1, ], "RAMP2"))))
  mergeCells(wb, i, str_which(tbl_in[1, ], "RAMP3"), rep(1, length(str_which(tbl_in[1, ], "RAMP3"))))
}

saveWorkbook(wb, sum_tbl_name, overwrite = T)
```


Upset plots of interactions
---------------------------

Figure 3A

```{r}
upset_epi <- cxdet_ramp_upset(cxdet_cd_sep$interaction_evidence, set_sizes = F, name = NULL,
                              matrix = intersection_matrix(geom = geom_point(size = 1.5),
                                                           segment = geom_segment(size = 0.25)),
                              # Set same y axis scales for the two plots
                              base_annotations = list(
                                "Intersection size" = intersection_size(text = list(size = 2)) +
                                  ylim(0, 60) + theme(axis.text = element_text(size = 8),
                                                      axis.title = element_text(size = 10),
                                                      panel.grid.major.x = element_blank())
                              ),
                              themes = upset_modify_themes(list(
                                'intersections_matrix' = theme(text = element_text(size = 8))
                              )),
                              height_ratio = 0.5) +
  labs(title = "Epitope capture") +
  theme(plot.title = element_text(hjust = 0.65, size = 10))
upset_hpa <- cxdet_ramp_upset(cxdet_dens_res$interaction_evidence, set_sizes = F, name = NULL,
                              # Remove some labels redundant labels that are the same in both plots
                              matrix = intersection_matrix(geom = geom_point(size = 1.5),
                                                           segment = geom_segment(size = 0.25)) + guides(y = "none"),
                              base_annotations = list(
                                "Intersection size" = intersection_size(text = list(size = 2)) +
                                  ylim(0, 60) + theme(axis.title = element_blank(),
                                                      axis.text = element_blank(),
                                                      panel.grid.major.x = element_blank())
                              ),
                              height_ratio = 0.5) +
  labs(title = "Protein capture") +
  theme(plot.title = element_text(hjust = 0.5, size = 10))
cxdet_upset <- upset_epi + upset_hpa + plot_layout(widths = c(1, 0.8))
```

```{r}
cxdet_upset_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_cxdet_upset_both.pdf")
ggsave(filename = cxdet_upset_name, plot = cxdet_upset, width = 7.25, height = 3, device = "pdf", useDingbats = F)
```

Epitope and GPCR capture complex evidence matrix
------------------------------------------------

```{r}
data.frame("Strong" = c("Yes", "Yes", "Maybe"),
           "Medium" = c("Yes", "Maybe", "No"),
           "Weak" = c("Maybe", "No", "No")) %>%
    `rownames<-`(c("Strong", "Medium", "Weak"))
# Put together epitope and protein capture and get only those with strong/strong, strong/medium, weak/medium, or weak/weak evidences of interaction if there are validated antibodies. If no validated antibodies, strong is yes and weak is no, skip medium
epi_prot_evid_matrix <- rbind(
  cxdet_cd_sep$interaction_evidence %>%
    select(contains("which"), int_evid) %>%
    mutate(capt = "epitope"),
  cxdet_dens_res$interaction_evidence %>%
    select(contains("which"), int_evid) %>%
    mutate(capt = "protein")
) %>%
  pivot_wider(id_cols = c(which_gpcr, which_ramp), names_from = capt, values_from = int_evid) %>%
  group_by(which_gpcr, which_ramp) %>%
  # filter(!(epitope == "Strong" & protein == "Weak"),
  #        !(epitope == "Medium" & protein == "Medium"),
  #        !(epitope == "Weak" & protein == "Strong")) %>%
  mutate(class = case_when(
    epitope == "Strong" & protein == "Weak" ~ "Medium",
    epitope == "Weak" & protein == "Strong" ~ "Medium",
    epitope == "Medium" & protein == "Medium" ~ "Medium",
    epitope == "Medium" & is.na(protein) ~ "Medium",
    "Strong" %in% c(epitope, protein) ~ "Yes",
    "Weak" %in% c(epitope, protein) ~ "No",
    epitope == "Strong" & is.na(protein) ~ "Yes",
    epitope == "Weak" & is.na(protein) ~ "No")) %>%
  filter(!is.na(class)) %>%
  filter(class != "Medium") %>%
  ungroup()

# Also classify based on whether a GPCR interacts with any RAMP or not
gpcr_any_int <- epi_prot_evid_matrix %>%
  group_by(which_gpcr) %>%
  summarise(any_int = case_when(any("Yes" %in% class) ~ "Yes", T ~ "No")) %>%
  ungroup()

```

Arrestin and G protein statistics
---------------------------------

figure S13 (A, B, C)

```{r}
# Get arrestin and G-protein family annotations
# Annotations downloaded from GPCRdb
# Look at log(Emax/EC50), convert to a binary classification
arr_dat <- read_excel("arrestin_coupling.xlsx") %>%
  filter(!is.na(group)) %>% select(uniprot, contains("log")) %>%
  mutate(across(contains("log"), .fns = function(x) {
    case_when(as.numeric(x) == 0 ~ 0, as.numeric(x) != 0 ~ 1)
  }))
gprot_dat <- read_excel("families_coupling.xlsx") %>%
  filter(!is.na(group), biosensor == "Mean") %>% select(uniprot, contains("guide")) %>%
  # Remove dashes
  mutate(across(contains("guide"), .fns = function(x) {
    # Use case_when to be able to introduce NAs
    case_when(x != "-" ~ x)
  }))
gprot_dat$n_prim <- apply(gprot_dat, 1, function(x) {
  sum(x == "1'", na.rm = T)
})
gprot_dat$n_sec <- apply(gprot_dat, 1, function(x) {
  sum(x == "2'", na.rm = T)
})

# Add new info to any int data
gpcr_any_int <- gpcr_any_int %>% left_join(arr_dat, by = c("which_gpcr" = "uniprot")) %>%
  left_join(gprot_dat, by = c("which_gpcr" = "uniprot"))

arr_gprot_pie <- function(dat_in, fill_name = NULL) {
  # Get p-values
  dat_p <- dat_in %>%
    group_by(value) %>% nest() %>%
    mutate(p = map(data, ~ {
      fisher.test(.x$name, .x$any_int)$p.value
    })) %>%
    select(-data) %>%
    unnest(p)
  
  # Get counts for plotting
  dat_counts <- dat_in %>%
    count(name, any_int, value) %>%
    mutate(percent = n / sum(n) * 100, n_tot = paste0(n, "/", sum(n)), .by = c(any_int, value)) %>%
    # P-value things
    left_join(dat_p, by = "value") %>%
    mutate(x1 = 101, x2 = 103, y1 = 1, y2 = 2, x_bar = 103, x_text = 108, y_text = 1.5) %>%
    mutate(pstar = p_to_star(p))
  
  # Plot differently depending on whether there are multiple levels or not (facet if more than one)
  lab_pos <- dat_counts %>%
    group_by(any_int, value) %>%
    mutate(csum = rev(cumsum(rev(percent))), 
           pos = percent / 2 + lead(csum, 1),
           pos = if_else(is.na(pos), percent / 2, pos))

  dat_plt <- dat_counts %>%
    ggplot(aes(x = "", y = percent, fill = name)) +
    geom_bar(stat = "identity", colour = "black", width = 1) +
    ggrepel::geom_label_repel(aes(y = pos, label = paste0("N: ", n_tot, "\n(", signif(percent, 3), "%)")),
                              size = 2, nudge_x = 1, data = lab_pos,
                              show.legend = F, segment.size = 0.2) +
    scale_fill_brewer(palette = "Accent", direction = 1) +
    labs(x = "Percent", y = "Any RAMP interaction", fill = fill_name) +
    facet_grid(cols = vars(any_int)) +
    coord_polar(theta = "y") +
    theme_void() +
    theme(strip.text.y = element_text(size = 14, angle = -90),
          strip.text.x = element_text(size = 14))
  
    if (length(unique(dat_counts$value)) > 1) {dat_plt <- dat_plt + facet_grid(cols = vars(any_int), rows = vars(value))}
    
  return(list("plt" = dat_plt, "counts" = dat_counts, "p" = dat_p))
}

# Make plots showing distributions within yes/no groups
arr_values <- gpcr_any_int %>%
  select(which_gpcr, any_int, contains("arr")) %>%
  filter(!is.na(arrb1_log)) %>%
  pivot_longer(cols = -c(which_gpcr, any_int)) %>%
  filter(value == 1) %>%
  mutate(name = case_when(name == "arrb1_log" ~ "\u03B2arrestin1",
                          name == "arrb2_log" ~ "\u03B2arrestin2",
                          name == "arrb2_no_grk_log" ~ "\u03B2arrestin2,\nno GRK")) %>%
  mutate(any_int = factor(any_int, levels = c("Yes", "No")))

arr_plt <- arr_gprot_pie(arr_values, "\u03B2Arrestin")

# Gprotein
gprot_values <- gpcr_any_int %>%
  select(which_gpcr, any_int, contains("guide")) %>%
  pivot_longer(cols = -c(which_gpcr, any_int)) %>%
  filter(!is.na(value)) %>%
  mutate(name = case_when(str_detect(name, "gi_o") ~ "Gi/o",
                          str_detect(name, "gq_11") ~ "Gq/11",
                          str_detect(name, "g12_13") ~ "G12/13",
                          str_detect(name, "gs") ~ "Gs")) %>%
  mutate(value = case_when(value == "1'" ~ "Primary",
                           value == "2'" ~ "Secondary")) %>%
  mutate(any_int = factor(any_int, levels = c("Yes", "No")))

gprot_plt <- arr_gprot_pie(gprot_values, "G protein")

gprot_n_values <- gpcr_any_int %>%
  select(which_gpcr, any_int, n_prim, n_sec) %>%
  mutate(any_int = factor(any_int, levels = c("Yes", "No")))

gprot_prim <- arr_gprot_pie(gprot_n_values %>% select(-n_sec) %>% rename(name = n_prim) %>%
                              mutate(value = 1, name = as.character(name)) %>%
                              filter(!is.na(name)),
                            fill_name = "Number of\nprimary\ncouplings")

gprot_sec <- arr_gprot_pie(gprot_n_values %>% select(-n_prim) %>% rename(name = n_sec) %>%
                              mutate(value = 1, name = as.character(name)) %>%
                              filter(!is.na(name)),
                            fill_name = "Number of\nsecondary\ncouplings")

# Table over number of yes/no and how many have any information on coupling
yn <- gpcr_any_int %>%
  group_by(which_gpcr) %>%
  mutate(arr_info = case_when(any(c(!is.na(arrb1_log), !is.na(arrb2_no_grk_log), !is.na(arrb2_log))) ~ "Yes", T ~ "No"),
         gprot_info = case_when(any(c(!is.na(guide_to_pharm_gs), !is.na(guide_to_pharm_gi_o), !is.na(guide_to_pharm_gq_11), !is.na(guide_to_pharm_g12_13))) ~ "Yes", T ~ "No")) %>%
  ungroup() %>%
  count(any_int, arr_info, gprot_info) %>%
  group_by(any_int) %>%
  mutate(percent_by_any_int = n / sum(n) * 100)

```

```{r}
arr_gprot_combined <- gprot_plt$plt /
  gprot_prim$plt /
  arr_plt$plt +
  plot_layout(heights = c(2, 1, 1)) +
  plot_annotation(tag_levels = "A", theme = theme(plot.tag = element_text(size = 18)))

ggsave(filename = paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_arrestin_gprot.pdf"), plot = arr_gprot_combined, height = 9, width = 7.25-1, device = cairo_pdf)

```

Interaction and expression
--------------------------

RAMP expression vs interaction (figure S6, A and B)

```{r}
ramp_qrt_plts <- quartile_plots(rdat$long_dat_all, cxdet_cd_sep$interaction_evidence, cxdet_dens_res$interaction_evidence) %>%
  wrap_plots(ncol = 1, guides = "collect")
```

```{r}
ramp_qrt_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_cxdet_ramp_quartiles.pdf")
ggsave(filename = ramp_qrt_name, plot = ramp_qrt_plts, width = 7.3, height = 5)
```

GPCR expression vs interaction (Figure S6, C and D)

```{r}
gpcr_qrt_plts <- quartile_plots(rdat$long_dat_all, cxdet_cd_sep$interaction_evidence, cxdet_dens_res$interaction_evidence, "GPCR") %>%
  wrap_plots(ncol = 1, guides = "collect")
```

```{r}
gpcr_qrt_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_cxdet_gpcr_quartiles.pdf")
ggsave(filename = gpcr_qrt_name, plot = gpcr_qrt_plts, width = 7.3, height = 5)
```

Split into each capture-detection scheme (Figure S7, A and B)

```{r}
ramp_qrt_split <- quartile_plt_per_capt(rdat$long_dat_all, cxdet_cd_sep$interactions %>% mutate(pass = case_when(pass == "1" ~ "Pass", pass == "0" ~ "Fail")),
                                        cxdet_dens_res$interaction_evidence, "RAMP")
gpcr_qrt_split <- quartile_plt_per_capt(rdat$long_dat_all, cxdet_cd_sep$interactions %>% mutate(pass = case_when(pass == "1" ~ "Pass", pass == "0" ~ "Fail")),
                                        cxdet_dens_res$interaction_evidence, "GPCR")
```


```{r}
ramp_qrt_split_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_ramp_quartile_split.pdf")
ggsave(filename = ramp_qrt_split_name, plot = ramp_qrt_split, width = 7.3, height = 5)

gpcr_qrt_split_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_gpcr_quartile_split.pdf")
ggsave(filename = gpcr_qrt_split_name, plot = gpcr_qrt_split, width = 7.3, height = 5)
```


QC plots
--------

```{r pilot plot data}
pilot_file <- "pilot_plate.xlsx"

# Binder info
pilot_binder <- read_excel(pilot_file, sheet = 2)

# MFI
pilot_mfi <- read_excel(pilot_file, sheet = 4)
```

Figure S2 (B and C), Figure S3

```{r pilot barplots}
pilot_barplt <- pilot_mfi %>%
  # Get CALCRL and mock-mock samples
  filter(GPCR_comment == "CALCRL_old_v2" | (GPCR == "mock" & interactor == "mock")) %>%
  select(GPCR_comment, interactor_comment, detection_ab,
         contains("1D4"), contains("ollas"), contains("FLAG"), contains("HA"), contains("CALCRL"), contains("RAMP3"), contains("Bare")) %>%
  # Turn into numeric class
  mutate(`M anti-HA.308` = as.numeric(`M anti-HA.308`)) %>%
  # Add column for sample names
  unite("samp", GPCR_comment, interactor_comment, sep = ".") %>%
  # Get mean of HA beads (same binder)
  mutate(HA = rowMeans(select(., `M anti-HA.292`, `M anti-HA.308`))) %>%
  select(-c(`M anti-HA.292`, `M anti-HA.308`)) %>%
  # Rename binders to be more concise
  rename_with(.fn = function(x) {
    new_name <- case_when(grepl("1D4", x) ~ "1D4",
                          grepl("Ollas", x) ~ "OLLAS",
                          grepl("FLAG", x) ~ "FLAG",
                          grepl("CALCRL", x) ~ "CALCRL",
                          grepl("RAMP3", x) ~ "RAMP3",
                          grepl("Bare", x) ~ "Bare bead",
                          T ~ x)
    return(new_name)
  }) %>%
  pivot_longer(cols = -c(samp, detection_ab), names_to = "binder", values_to = "MFI") %>%
  # Reorder facets
  mutate(binder = factor(binder, levels = c("Bare bead", "CALCRL", "RAMP3", "1D4", "OLLAS", "FLAG", "HA"))) %>%
  # New labels for x-axis groups
  # RAMP3_old: construct 1, has FLAG and OLLAS tags
  # RAMP3: construct 2, has 3HA and OLLAS tags
  mutate(new_col = case_when(grepl("RAMP3_old", samp, ignore.case = T) ~ "1",
                             grepl("RAMP3$", samp) ~ "2",
                             T ~ "Mock")) %>%
  mutate(samp = factor(samp, levels = sort(unique(samp), decreasing = T)),
         new_col = factor(new_col, levels = c("Mock", "1", "2"))) %>%
  # Plot with log2 of ratios between signal and mock
  group_by(detection_ab, binder) %>%
  mutate(MFI = log2(MFI / MFI[samp == "mock.mock"])) %>%
  ungroup() %>%
  # Skip 1D4 capture with 1D4 detection and OLLAS capture with OLLAS detection, skip mock
  filter(detection_ab != binder, samp != "mock.mock") %>%
  group_by(detection_ab) %>%
  nest() %>%
  mutate(plt = map(data, ~ {
    plt_out <- .x %>%
      mutate(detab = detection_ab) %>%
      ggplot() +
      geom_bar(aes(x = new_col, y = MFI), stat = "identity", width = 0.75) +
      geom_hline(yintercept = -Inf, size = 2.5) +
      geom_vline(xintercept = -Inf, size = 2.5) +
      facet_grid(detab ~ binder) +
      labs(x = "RAMP3 construct", fill = "Interactor") +
      ylim(0, 8.5) +
      theme_classic() +
      theme(axis.line = element_blank(),
            axis.text.x = element_text(size = 18, colour = "black"),
            axis.text.y.left = element_text(size = 18, colour = "black"),
            axis.ticks = element_line(size = 2, colour = "black"),
            axis.title.y = element_blank(),
            axis.title.x = element_text(size = 18),
            strip.text = element_text(size = 18),
            strip.background = element_rect(size = 2),
            legend.title = element_text(size = 18),
            legend.text = element_text(size = 18))
    
    if (detection_ab == "1D4") {
      plt_out <- plt_out +
        labs(title = "Capture") +
        theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank(),
              plot.title = element_text(hjust = 0.5, size = 18))
    }
    
    return(plt_out)
  })) %>%
  pull(plt)

# Due to removing 1D4 capture w/ 1D4 detection and OLLAS capture w/ OLLAS detection, some facets become empty if using facet_grid,
# or the facet labels all end up on the top instead of some of them on the top and some of them to the right
# To remove the empty facets while keeping labels on the right, the data is split along one facet dimension (detection_ab) and then
# pasted together using the patchwork package.
# To add axis annotation on the left and facet annotation on the right (if faceting normally: fixed automatically and added by forcing a second y axis, respectively),
# text only plots are added on both sides of the plots, again with the patchwork package
# Thanks to guides = "collect", the annotation on the right ends up on the left of the legend
text_left <- ggplot(data.frame(a = "2-Fold change", x = 1, y = 1)) +
  geom_text(aes(x = x, y = y, label = a), angle = 90, size = 7) +
  theme_void() +
  coord_cartesian(clip = "off")
text_right <- ggplot(data.frame(a = "Detection", x = 1, y = 1)) +
  geom_text(aes(x = x, y = y, label = a), angle = -90, size = 7) +
  theme_void() +
  coord_cartesian(clip = "off")

barplt_out <- text_left + (pilot_barplt[[1]] / pilot_barplt[[2]]) + text_right +
  plot_layout(widths = c(1, 25, 1), guides = "collect")

# Compare CALCRL with different tags
pilot_barplt2 <- pilot_mfi %>%
  filter((GPCR_comment %in% c("CALCRL_old", "CALCRL_old_v2") & interactor_comment == "RAMP3") |
         (GPCR_comment == "mock" & interactor_comment == "mock")) %>%
  select(GPCR_comment, interactor_comment, detection_ab,
         contains("1D4"), contains("ollas"), contains("FLAG"), contains("HA"), contains("CALCRL"), contains("RAMP3"), contains("Bare")) %>%
  # Turn into numeric class
  mutate(`M anti-HA.308` = as.numeric(`M anti-HA.308`)) %>%
  # Add column for sample names
  unite("samp", GPCR_comment, interactor_comment, sep = ".") %>%
  # Get mean of HA beads (same binder)
  mutate(HA = rowMeans(select(., `M anti-HA.292`, `M anti-HA.308`))) %>%
  select(-c(`M anti-HA.292`, `M anti-HA.308`)) %>%
  # Rename binders to be more concise
  rename_with(.fn = function(x) {
    new_name <- case_when(grepl("1D4", x) ~ "1D4",
                          grepl("Ollas", x) ~ "OLLAS",
                          grepl("FLAG", x) ~ "FLAG",
                          grepl("CALCRL", x) ~ "CALCRL",
                          grepl("RAMP3", x) ~ "RAMP3",
                          grepl("Bare", x) ~ "Bare bead",
                          T ~ x)
    return(new_name)
  }) %>%
  pivot_longer(cols = -c(samp, detection_ab), names_to = "binder", values_to = "MFI") %>%
  # Reorder facets
  mutate(binder = factor(binder, levels = c("Bare bead", "CALCRL", "RAMP3", "1D4", "OLLAS", "FLAG", "HA"))) %>%
  # New labels for x-axis groups
  # old: construct 1, with HA and 1D4 tags
  # old_v2: construct 2, with FLAG and 1D4 tags
  mutate(new_col = case_when(grepl("old_v2\\.", samp, ignore.case = T) ~ "2",
                             grepl("old\\.", samp) ~ "1",
                             T ~ "Mock")) %>%
  mutate(samp = factor(samp, levels = sort(unique(samp), decreasing = T)),
         new_col = factor(new_col, levels = c("Mock", "1", "2"))) %>%
  # Plot with log2 fold change
  group_by(detection_ab, binder) %>%
  mutate(MFI = log2(MFI / MFI[samp == "mock.mock"])) %>%
  ungroup() %>%
  # Skip 1D4 capture with 1D4 detection and OLLAS capture with OLLAS detection
  filter(detection_ab != binder, samp != "mock.mock") %>%
  # Skip samples where both the CALCRL and the RAMP have the tag being captured, and where none of them have it
  group_by(detection_ab) %>%
  nest() %>%
  mutate(plt = map(data, ~ {
    plt_out <- .x %>%
      mutate(detab = detection_ab) %>%
      ggplot() +
      geom_bar(aes(x = new_col, y = MFI), stat = "identity", width = 0.75) +
      geom_hline(yintercept = -Inf, size = 2.5) +
      geom_vline(xintercept = -Inf, size = 2.5) +
      facet_grid(detab ~ binder) +
      labs(x = "CALCRL construct", fill = "GPCR") +
      ylim(0, 8.5) +
      theme_classic() +
      theme(axis.line = element_blank(),
            axis.text.x = element_text(size = 18, colour = "black"),
            axis.text.y.left = element_text(size = 18, colour = "black"),
            axis.ticks = element_line(size = 2, colour = "black"),
            axis.title.y = element_blank(),
            axis.title.x = element_text(size = 18),
            strip.text = element_text(size = 18),
            strip.background = element_rect(size = 2),
            legend.title = element_text(size = 18),
            legend.text = element_text(size = 18))
    
    if (detection_ab == "1D4") {
      plt_out <- plt_out +
        labs(title = "Capture") +
        theme(axis.ticks.x = element_blank(), axis.text.x = element_blank(), axis.title.x = element_blank(),
              plot.title = element_text(hjust = 0.5, size = 18))
    }
    
    return(plt_out)
  })) %>%
  pull(plt)

barplt_out2 <- text_left + (pilot_barplt2[[1]] / pilot_barplt2[[2]]) + text_right +
  plot_layout(widths = c(1, 25, 1), guides = "collect")

```


```{r pilot boxplots}
# Boxplots
pilot_boxes <- pilot_mfi %>%
  filter((GPCR_comment == "GPRC5A" & interactor_comment %in% c("mock", "RAMP2")) |
             (GPCR_comment == "HCRTR2" & interactor_comment %in% c("mock", "RAMP3"))) %>%
  select(GPCR_comment, interactor_comment, detection_ab,
         contains("Ollas"), contains("HA"), contains("FLAG"), contains("1D4")) %>%
  # Convert to number to be able to pivot
  mutate(`M anti-HA.308` = as.numeric(`M anti-HA.308`)) %>%
  # Create sample names
  unite("samp", GPCR_comment, interactor_comment, sep = ".", remove = F) %>%
  pivot_longer(cols = -c(samp, GPCR_comment, interactor_comment, detection_ab),
               names_to = "binder", values_to = "MFI") %>%
  # Make more concise binder names (and combine HA beads in the process)
  mutate(binder = case_when(grepl("1D4", binder) ~ "1D4",
                            grepl("Ollas", binder) ~ "OLLAS",
                            grepl("FLAG", binder) ~ "FLAG",
                            grepl("HA", binder) ~ "HA",
                            T ~ binder)) %>%
  # Look at complex-forming combinations
  filter((binder %in% c("OLLAS", "HA") & detection_ab == "1D4") |
             (binder %in% c("1D4", "FLAG") & detection_ab == "OLLAS")) %>%
  mutate(binder = factor(binder, levels = c("OLLAS", "HA", "1D4", "FLAG"))) %>%
  # Make simpler axis labels
  mutate(samp = str_extract(samp, "mock|RAMP\\d")) %>%
  # By GPCR and detab
  group_by(detection_ab, GPCR_comment) %>%
  nest() %>%
  mutate(plt = map(data, ~ {
    plt_range <- c(4.7, 13.5)
    plt_diff <- diff(plt_range)
    
    # One-sided wilcoxon test to check if mock is lower than samples with RAMP
    wilcox_test <- sapply(unique(.x$binder), function(b) {
      wt <- wilcox.test(.x %>% filter(str_detect(interactor_comment, "RAMP"), binder == b) %>% pull(MFI),
                        .x %>% filter(str_detect(interactor_comment, "mock"), binder == b) %>% pull(MFI),
                        paired = F, alternative = "greater")
      
      return(list("df" = data.frame("binder" = b,
                                    "p.value" = wt$p.value,
                                    "stat" = wt$stat),
                  "test" = wt))
    }, simplify = F)
    
    wilcox_p <- lapply(wilcox_test, function(y) {y$df}) %>%
      rbindlist() %>%
      left_join(.x, by = "binder") %>%
      group_by(binder) %>%
      summarise(binder = unique(binder), p.value = unique(p.value), statistic = unique(stat),
                y_max = log2(max(MFI)), y_pos = log2(max(MFI)) + 0.13 * plt_diff) %>%
      mutate(p = p_to_star(p.value)) %>%
      mutate(x_pos = 1.5) %>%
      mutate(gpcr = GPCR_comment)
     
    lines_df <- rbind(wilcox_p %>% mutate(x1 = 1, x2 = 2, y1 = y_max + 0.1 * plt_diff, y2 = y_max + 0.1 * plt_diff),
                      wilcox_p %>% mutate(x1 = 1, x2 = 1, y1 = y_max + 0.05 * plt_diff, y2 = y_max + 0.1 * plt_diff),
                      wilcox_p %>% mutate(x1 = 2, x2 = 2, y1 = y_max + 0.05 * plt_diff, y2 = y_max + 0.1 * plt_diff))

    p <- ggplot(.x, aes(x = samp, y = log2(MFI))) +
        stat_summary(fun = median, fun.min = median, fun.max = median,
                     geom = "errorbar", colour = "grey30", width = 0.4, size = 1.3) +
        stat_summary(fun = median,
                     fun.min = function(a) quantile(a, 0.25),
                     fun.max = function(a) quantile(a, 0.75),
                     geom = "errorbar", colour = "grey30", width = 0.25, size = 1.0) +
        geom_beeswarm(aes(colour = samp), show.legend = F, size = 3) +
        geom_hline(yintercept = -Inf, linewidth = 2.5) + geom_vline(xintercept = -Inf, linewidth = 2.5) +
        geom_text(aes(x = x_pos, y = y_pos, label = p), data = wilcox_p %>% distinct(x_pos, y_pos, p, .keep_all = T) %>% select(x_pos, y_pos, p, binder), size = 9) +
        geom_segment(aes(x = x1, xend = x2, y = y1, yend = y2), data = lines_df) +
        facet_wrap(~ binder, drop = T, nrow = 1, scales = "free_x") +
        scale_colour_manual(values = c("grey75", "grey60")) +
        labs(x = NULL, y = paste0("Anti-", detection_ab, " log2(MFI)")) +
        # Account for height increase from p-value text
        ylim(plt_range) +
        theme_classic() +
        theme(axis.line = element_blank(),
              axis.text.x = element_text(size = 20, colour = "black"),
              axis.title = element_text(size = 20),
              axis.text.y = element_text(size = 20, colour = "black"),
              axis.ticks = element_line(size = 2),
              strip.text = element_text(size = 20),
              strip.background = element_rect(size = 2))

    # Title + remove axis text for top plots
    if (detection_ab == "1D4") {
      p <- p + labs(title = GPCR_comment) + theme(plot.title = element_text(hjust = 0.5, size = 24),
                                                  axis.text.x = element_blank(), axis.ticks.x = element_blank())
    }

    return(list("wilcox_test" = wilcox_test, "wilcox_p" = wilcox_p, "plots" = p))
  }))

pilot_box_p <- lapply(pilot_boxes$plt, function(x) {as.data.frame(x$wilcox_p)}) %>% data.table::rbindlist() %>%
  select(gpcr, binder, p.value, statistic)
pilot_boxplt <- lapply(pilot_boxes$plt, function(x) {x$plots}) %>% wrap_plots(nrow = 2)


```

```{r save pilot plots}
pilot_bar_fn <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_pilot_bar_ramp3.pdf")
ggsave(filename = pilot_bar_fn, plot = barplt_out, height = 6.5, width = 7.3*2, device = "pdf", useDingbats = F)

pilot_bar2_fn <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_pilot_bar_calcrl.pdf")
ggsave(filename = pilot_bar2_fn, plot = barplt_out2, height = 6.5, width = 7.3*2, device = "pdf", useDingbats = F)

pilot_box_fn <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_pilot_box.pdf")
ggsave(filename = pilot_box_fn, plot = pilot_boxplt, height = 4*2, width = 7.3*2, device = "pdf", useDingbats = F)

```

Pilot plots saved as `r pilot_bar_fn` and `r pilot_box_fn`. 

Expression validation of positive control
-----------------------------------------

Figure S4 (B and C)

```{r}
plt_range <- c(3.9, 15)
textsize <- 11
extra_theme <- theme(axis.line = element_blank(),
                     axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1, size = textsize, colour = "black"),
                     axis.text.y = element_text(size = textsize, colour = "black"),
                     axis.title = element_text(size = textsize),
                     strip.text = element_text(size = 9),
                     strip.background = element_rect(size = 1.5, linetype = "solid", colour = "black"),
                     axis.ticks = element_line(size = 0.5))

# Complex (capture and detection on different sides)
posctrl1_dat <- rdat$long_dat_all %>%
  filter((gene_name %in% c("RAMP1", "M anti-HA", "Ollas") & detection_ab == "1D4") |
         (gene_name %in% c("CALCRL", "M anti-FLAG", "1D4") & detection_ab == "OLLAS")) %>%
  filter(gpcr_interactor %in% c("empty.empty", "mock.mock", "CALCRL.RAMP1.posctrl")) %>%
  filter(sample_type != "gpcr.p11") %>%
  # Facet and x-axis orders
  mutate(gene_name = str_remove(gene_name, "M anti-") %>% toupper() %>% paste0(., " capture"),
         gene_name = factor(gene_name, levels = paste0(c("RAMP1", "HA", "OLLAS", "CALCRL", "FLAG", "1D4"), " capture")),
         gpcr_interactor = str_remove(gpcr_interactor, "\\.posctrl"),
         gpcr_interactor = factor(gpcr_interactor, levels = c("empty.empty", "mock.mock", "CALCRL.RAMP1"))) %>%
  select(gpcr_interactor, gene_name, detection_ab, value)

posctrl1_tests <- posctrl1_dat %>%
  group_by(detection_ab, gene_name) %>%
  nest() %>%
  mutate(p = map(data, ~ {
    # Anova
    ap <- summary(aov(value ~ gpcr_interactor, data = .x))[[1]] %>% as.data.frame() %>% mutate(Capture = str_remove(gene_name, " capture"))
    
    # Dunnett's multiple comparison test
    dp <- DunnettTest(x = .x$value, g = as.factor(.x$gpcr_interactor), control = "mock.mock")$mock.mock %>%
      as.data.frame() %>% rownames_to_column("gpcr_interactor") %>%
      mutate(gpcr_interactor = str_remove(gpcr_interactor, "-mock.mock")) %>%
      mutate(capture = str_remove(gene_name, " capture"),
             detection = detection_ab) %>%
      left_join(count(.x, gpcr_interactor), by = "gpcr_interactor")
    
    # y positions of labels
    p_ypos <- .x %>% filter(gpcr_interactor != "mock.mock") %>% group_by(gpcr_interactor) %>%
      summarise(ypos = max(log2(value), na.rm = T) + 0.05 * diff(plt_range)) %>% ungroup() %>%
      mutate("gene_name" = gene_name,
             "detection_ab" = detection_ab,
             "anova_p" = ap[1, 5],
             # NA if anova p >= 0.05
             "pval" = case_when(ap[1, 5] < 0.05 ~ dp[match(gpcr_interactor, dp$gpcr_interactor), "pval", drop = T]),
             "pstar" = p_to_star(pval))
    
    return(list("anova_p" = ap,
                "dunnett_p" = dp,
                "ypos" = p_ypos))
  })) %>%
  pull(p)

posctrl1_anova <- lapply(posctrl1_tests, function(x) {as.data.frame(x$anova_p)[1, ]}) %>% data.table::rbindlist()
posctrl1_dunnett <- lapply(posctrl1_tests, function(x) {x$dunnett_p}) %>% data.table::rbindlist()

posctrl1_p <- lapply(posctrl1_tests, function(x) {x$ypos}) %>%
  data.table::rbindlist() %>%
  # Avoid same name for detab column
  rename("detab" = "detection_ab")

posctrl1 <- posctrl1_dat %>%
  group_by(detection_ab) %>%
  nest() %>%
  mutate(plt = map(data, ~ {
    plt_out <- ggplot(.x %>% mutate(detab = paste0(detection_ab, " detection")), aes(x = gpcr_interactor, y = log2(value))) +
      geom_beeswarm(aes(colour = gpcr_interactor), show.legend = F, size = 1.5) +
      geom_text(aes(x = gpcr_interactor, y = ypos, label = pstar),
                posctrl1_p %>% filter(detab == detection_ab) %>% mutate(detab = paste0(detab, " detection")), size = 5) +
      scale_colour_manual(values = c("empty.empty" = "grey80", "mock.mock" = "grey75", "CALCRL.RAMP1" = "#BFEFFF")) +
      stat_summary(fun = median, fun.min = median, fun.max = median,
                   geom = "errorbar", colour = "grey50", width = 0.35, size = 0.8) +
      stat_summary(fun = median,
                   fun.min = function(a) quantile(a, 0.25),
                   fun.max = function(a) quantile(a, 0.75),
                   geom = "errorbar", colour = "grey50", width = 0.2, size = 0.65) +
      geom_hline(yintercept = -Inf, size = 1.5) + geom_vline(xintercept = -Inf, size = 1.5) +
      labs(x = NULL, y = "log2(MFI)") +
      ylim(plt_range) +
      facet_grid(cols = vars(gene_name), rows = vars(detab)) +
      theme_classic() +
      extra_theme
    
    # If upper plot, skip axis labels
    if (detection_ab == "1D4") {
      plt_out <- plt_out + theme(axis.text.x = element_blank(),
                                 axis.ticks.x = element_blank())
    }
    
    return(plt_out)
  })) %>%
  pull(plt) %>%
  wrap_plots(nrow = 2)

# Single molecules (capture and detection on same side)
posctrl2_dat <- rdat$long_dat_all %>%
  filter((gene_name %in% c("CALCRL", "M anti-FLAG") & detection_ab == "1D4") |
         (gene_name %in% c("RAMP1", "M anti-HA") & detection_ab == "OLLAS")) %>%
  filter(gpcr_interactor %in% c("empty.empty", "mock.mock", "CALCRL.RAMP1.posctrl")) %>%
  filter(sample_type != "gpcr.p11") %>%
  mutate(gene_name = str_remove(gene_name, "M anti-") %>% paste0(., " capture"),
         gene_name = factor(gene_name, levels = paste0(c("CALCRL", "FLAG", "RAMP1", "HA"), " capture")),
         gpcr_interactor = str_remove(gpcr_interactor, "\\.posctrl"),
         gpcr_interactor = factor(gpcr_interactor, levels = c("empty.empty", "mock.mock", "CALCRL.RAMP1"))) %>%
  select(gpcr_interactor, gene_name, detection_ab, value)

posctrl2_tests <- posctrl2_dat %>%
  group_by(detection_ab, gene_name) %>%
  nest() %>%
  mutate(p = map(data, ~ {
    # Anova
    ap <- summary(aov(value ~ gpcr_interactor, data = .x))[[1]] %>% as.data.frame() %>% mutate(Capture = str_remove(gene_name, " capture"))
    
    # Dunnett's multiple comparison test
    dp <- DunnettTest(x = .x$value, g = as.factor(.x$gpcr_interactor), control = "mock.mock")$mock.mock %>%
      as.data.frame() %>% rownames_to_column("gpcr_interactor") %>% mutate(gpcr_interactor = str_remove(gpcr_interactor, "-mock.mock")) %>%
      mutate(capture = str_remove(gene_name, " capture"),
             detection = detection_ab) %>%
      left_join(count(.x, gpcr_interactor), by = "gpcr_interactor")
    
    # y positions of labels
    p_ypos <- .x %>% filter(gpcr_interactor != "mock.mock") %>% group_by(gpcr_interactor) %>%
      summarise(ypos = max(log2(value), na.rm = T) + 0.05 * diff(plt_range)) %>% ungroup() %>%
      mutate("gene_name" = gene_name,
             "detection_ab" = detection_ab,
             "anova_p" = ap[1, 5],
             # NA if anova p >= 0.05
             "pval" = case_when(ap[1, 5] < 0.05 ~ dp[match(gpcr_interactor, dp$gpcr_interactor), "pval", drop = T]),
             "pstar" = p_to_star(pval))
    
    return(list("anova_p" = ap,
                "dunnett_p" = dp,
                "ypos" = p_ypos))
  })) %>%
  pull(p)

posctrl2_anova <- lapply(posctrl2_tests, function(x) {as.data.frame(x$anova_p)[1, ]}) %>% data.table::rbindlist()
posctrl2_dunnett <- lapply(posctrl2_tests, function(x) {x$dunnett_p}) %>% data.table::rbindlist()

posctrl2_p <- lapply(posctrl2_tests, function(x) {x$ypos}) %>%
  data.table::rbindlist() %>%
  # Avoid same name for detab column
  rename("detab" = "detection_ab")

posctrl2 <- posctrl2_dat %>%
  group_by(detection_ab) %>%
  nest() %>%
  mutate(plt = map(data, ~ {
    plt_out <- ggplot(.x %>% mutate(detab = paste0(detection_ab, " detection")), aes(x = gpcr_interactor, y = log2(value))) +
      geom_beeswarm(aes(colour = gpcr_interactor), show.legend = F, size = 1.5) +
      geom_text(aes(x = gpcr_interactor, y = ypos, label = pstar),
                posctrl2_p %>% filter(detab == detection_ab) %>% mutate(detab = paste0(detab, " detection")), size = 5) +
      scale_colour_manual(values = c("empty.empty" = "grey80", "mock.mock" = "grey75", "CALCRL.RAMP1" = "#BFEFFF")) +
      stat_summary(fun = median, fun.min = median, fun.max = median,
                   geom = "errorbar", colour = "grey50", width = 0.35, size = 0.8) +
      stat_summary(fun = median,
                   fun.min = function(a) quantile(a, 0.25),
                   fun.max = function(a) quantile(a, 0.75),
                   geom = "errorbar", colour = "grey50", width = 0.2, size = 0.65) +
      geom_hline(yintercept = -Inf, size = 1.5) + geom_vline(xintercept = -Inf, size = 1.5) +
      ylim(plt_range) +
      facet_grid(cols = vars(gene_name), rows = vars(detab)) +
      labs(x = NULL, y = "log2(MFI)") +
      theme_classic() +
      extra_theme
    
    # If upper plot, skip axis labels
    if (detection_ab == "1D4") {
      plt_out <- plt_out + theme(axis.text.x = element_blank(),
                                 axis.ticks.x = element_blank())
    }
    
    return(plt_out)
  })) %>%
  pull(plt) %>%
  wrap_plots(nrow = 2)

posctrl_plts <- wrap_plots(list(posctrl2, posctrl1), widths = c(2/5, 3/5))

```

```{r}
posctrl_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_posctrl_plt.pdf")
ggsave(filename = posctrl_name, plot = posctrl_plts, width = 7.3, height = 4, device = "pdf", useDingbats = F)
```


Plots from endogenous experiments
=================================

Often referred to as "validation" experiments and data below.

```{r}

# Exclude binders that did not pass validation
vd <- valid_dat # Keep HPA008070 for QC plots
np_binders <- rzdat$prot %>% filter(!pass) %>% pull(antibody)
valid_dat$data_list$prot <- valid_dat$data_list$prot %>% filter(!Antibody.name %in% np_binders)
valid_dat$data_list$mfi <- valid_dat$data_list$mfi %>% select(samp_name, !!valid_dat$data_list$prot$gene_name_id)
```

Max signal hits
---------------

Figure 3 (B and C)

```{r}
hit_check <- valid_hits(valid_dat, T)

# Make combined plots of selected plots
extra_plts <- function(dat, nrow, ncol) {
  # Find axis limits to use
  d <- dat %>% mutate(min = map(tbl, ~ {min(.x$mean_z)}),
                      max = map(tbl, ~ {max(.x$mean_z)}))
  lims <- c(min(unlist(d$min)), max(unlist(d$max)))
  
  # Put all plots into one with those limits
  wrap_plots(d$plt, nrow = nrow, ncol = ncol) & ylim(lims)
}

# One per RAMP
endog_plts <- sapply(paste0("RAMP", 1:3), function(x) {
  extra_plts(hit_check %>% filter(gpcr_ramp == "untransfected_untransfected", detection_ab == x) %>%
               arrange(cell_type), nrow = 1, ncol = 3)
}, simplify = F, USE.NAMES = T)

# Venn diagrams
hits <- hit_check %>% filter(gpcr_ramp == "untransfected_untransfected") %>%
  select(-plt, -tbl) %>% group_by(detection_ab) %>% nest() %>%
  mutate(hit_list = map(data, ~ {
    hits_out <- pull(.x, hits)
    names(hits_out) <- .x$cell_type
    
    return(hits_out)
  })) %>%
  pull(hit_list)
hit_venn <- lapply(seq_along(hits), function(x) {
  ggvenn(hits[[x]], names(hits[[x]]),
         stroke_color = switch(x, "1" = "#BFEFFF", "2" = "#B1E063", "3" = "#EEAD0E"),
         stroke_size = 1.75, fill_alpha = 0.25, text_size = 3, set_name_size = 5, show_percentage = T)
})

dsgn <- "
ABCD
EFGH
IJKL
"

hit_bsw_venn_plt <- wrap_plots(
  list(
    endog_plts[[1]][[1]] + labs(tag = "A") + labs(y = NULL) + theme(plot.title = element_text(size = 12, hjust = 0.5)),
    endog_plts[[1]][[2]] + labs(y = NULL) + theme(plot.title = element_text(size = 12, hjust = 0.5)),
    endog_plts[[1]][[3]] + labs(y = NULL) + theme(plot.title = element_text(size = 12, hjust = 0.5)),
    plot_spacer(),
    endog_plts[[2]][[1]] + labs(tag = "B", title = NULL, y = NULL),
    endog_plts[[2]][[2]] + labs(title = NULL, y = NULL),
    endog_plts[[2]][[3]] + labs(title = NULL, y = NULL),
    plot_spacer(),
    endog_plts[[3]][[1]] + labs(tag = "C", title = NULL, y = NULL),
    endog_plts[[3]][[2]] + labs(title = NULL, y = NULL),
    endog_plts[[3]][[3]] + labs(title = NULL, y = NULL),
    plot_spacer()
  ),
  design = dsgn
)

```

```{r}

for (i in 1:3) {
  plt_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_max_hits_venn_RAMP", i, ".pdf")
  pdf(file = plt_name, width = 3, height = 3, useDingbats = F)
  print(hit_venn[[i]])
  dev.off()
}

hit_bsw_venn_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_valid_bsw_venn.pdf")
ggsave(filename = hit_bsw_venn_name, plot = hit_bsw_venn_plt, height = 3.5, width = 7.25, device = "pdf", useDingbats = F)

```

Table S8

```{r}
# Save a table of hits
hit_tbl <- hit_check %>% select(detection_ab, cell_type, gpcr_ramp, tbl) %>% unnest(tbl) %>%
  filter(point_lab != "") %>% as.data.frame() %>% select(-point_lab) %>%
  filter(gpcr_ramp == "untransfected_untransfected") %>%
  group_by(detection_ab) %>% nest() %>% mutate(tbl = map(data, ~ {
    .x %>% pivot_wider(id_cols = binder, names_from = cell_type, values_from = mean_z) %>%
      left_join(valid_dat$data_list$prot %>% select(Gene, Antibody.name, gene_name_id), by = c("binder" = "gene_name_id")) %>%
      select(-binder) %>% relocate(Gene, Antibody.name) %>% rename(GPCR = Gene, Antibody = Antibody.name) %>%
      # Remove the AC144573.1 part of the ADRB3 Ab as it's the same Ab as the one in the main screen but there it only has ADRB3 as annotation
      mutate(GPCR = str_remove(GPCR, "AC144573\\.1;")) %>% arrange(GPCR)
  })) %>% select(-data)

# Make table with multiple tabs
tbl_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_validation_hits.xlsx")
write.xlsx(hit_tbl %>% pull(tbl) %>% setNames(hit_tbl$detection_ab), tbl_name, asTable = T, tableStyle = "TableStyleLight1")
```

Figure 3 (D)

```{r, fig.height=4, fig.width=7.3}
# Compare main screen to validation hits
# Mark how the GPCRs interacted in the endogenous analysis
cell_sym <- c("Expi" = "", "SH-SY5Y" = "", "SK-N-MC" = "")
hit_gpcrs <- hit_check %>% select(detection_ab, cell_type, gpcr_ramp, tbl) %>% unnest(tbl) %>%
  filter(point_lab != "") %>% as.data.frame() %>% select(-point_lab) %>% filter(gpcr_ramp == "untransfected_untransfected") %>%
  # Deal with a special case that contains a dot in the name (usually dots separate different GPCRs)
  mutate(target = str_remove(binder, "_\\d+") %>% str_replace("AC144573\\.", "AC144573_")) %>%
  separate_rows(target, sep = "\\.") %>%
  mutate(target = str_replace(target, "AC144573_", "AC144573.")) %>%
  group_by(detection_ab, target) %>%
  # Extra info to mark heatmap cells
  summarise(cells = unique(cell_type) %>% sort() %>%
              str_replace_all(., cell_sym) %>% paste0(collapse = ""),
            binders = paste0(unique(binder), collapse = ";"))

valid_hits_hm_dat <- rbind(
  cxdet_cd_sep$interaction_evidence %>% filter(which_gpcr %in% hit_gpcrs$target) %>% mutate(capt = "Epitope") %>% select(-fraction_pass),
  cxdet_dens_res$interaction_evidence %>% filter(which_gpcr %in% hit_gpcrs$target) %>% mutate(capt = "Protein") %>% select(-fraction_pass)
) %>% left_join(hit_gpcrs, by = c("which_gpcr" = "target", "which_ramp" = "detection_ab")) %>%
  mutate(int_evid = factor(int_evid, levels = c("Strong", "Medium", "Weak")),
         which_gpcr = factor(which_gpcr, levels = sort(unique(which_gpcr), decreasing = T))) %>%
  # Keep those with values for both epitope and protein capture
  group_by(which_gpcr) %>% filter(if (length(capt) < 4) {F} else {T}) %>% ungroup() %>% as.data.frame()
# Add a dummy variable that will allow creating a custom legend for the cell types
valid_hits_hm_dat$dummy <- c("Expi", "SH-SY5Y", "SK-N-MC")

gpcr_order <- valid_hits_hm_dat %>%
  mutate(int_sc = case_when(int_evid == "Strong" ~ 3, int_evid == "Medium" ~ 2, int_evid == "Weak" ~ 1)) %>%
  group_by(which_gpcr) %>%
  summarise(sc = sum(int_sc)) %>%
  arrange(desc(sc)) %>%
  pull(which_gpcr)

valid_hits_hm <- valid_hits_hm_dat %>%
  # Arrange by strongest interaction evidence
  mutate(which_gpcr = factor(which_gpcr, levels = gpcr_order)) %>%
  ggplot(aes(x = which_gpcr, y = capt)) +
  geom_tile(aes(fill = int_evid), colour = "white") +
  geom_text(aes(label = cells, alpha = dummy), size = 2.5) +
  facet_wrap(~ which_ramp, ncol = 1) +
  scale_fill_brewer(palette = "Set2") +
  scale_alpha_manual("Cell type", values = 1:3,
                     guide = guide_legend(override.aes = list(size = 5,
                                                              fill = "white",
                                                              label = cell_sym))) +
  labs(x = "GPCR", y = "Capture", fill = "Evidence of\ninteraction") +
  theme_minimal() +
  theme(axis.title = element_text(size = 10),
        strip.text = element_text(size = 10),
        axis.text.x = element_text(size = 8, colour = "black", angle = 45, hjust = 1, vjust = 1),
        axis.text.y = element_text(size = 8, colour = "black"),
        legend.text = element_text(size = 8),
        legend.title = element_text(size = 8))

```

```{r}
valid_hm_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_validation_hits_hm.pdf")
ggsave(filename = valid_hm_name, plot = valid_hits_hm, width = 6.25, height = 3, device = cairo_pdf)
```

CALCRL check
------------

Figure S8

```{r}
valid_clr_dat <- vd$data_list$mfi %>%
  # Look at the two CALCRL binders
  select(samp_name, contains("CALCRL")) %>%
  # Add sample information
  left_join(vd$data_list$well_info %>%
              select(samp_name, exclude, cell_type, gpcr, ramp, detection_ab), by = "samp_name") %>%
  # Only look at empty samples and Expi samples
  filter(is.na(exclude), cell_type %in% c("buffer", "Expi"), gpcr %in% c("CALCRL")) %>%
  select(-exclude, -cell_type) %>%
  unite("gpcr_ramp", gpcr, ramp, sep = ".") %>%
  pivot_longer(cols = -c(samp_name, gpcr_ramp, detection_ab), names_to = "binder", values_to = "value") %>%
  # Add antibody names
  left_join(vd$data_list$prot %>%
              select(Antibody.name, Gene, gene_name_id), by = c("binder" = "gene_name_id")) %>%
  unite("antibody", Gene, Antibody.name) %>%
  # Set x-axis order
  mutate(gpcr_ramp = str_remove(gpcr_ramp, "CALCRL\\.") %>% str_replace("mock", "Mock"),
         gpcr_ramp = factor(gpcr_ramp, levels = c("Mock", "RAMP1", "RAMP2", "RAMP3")))

# Anova and Dunnett test against CALCRL.mock
valid_clr_test <- valid_clr_dat %>%
  group_by(antibody, detection_ab) %>%
  nest() %>%
  mutate(anova = map(data, ~ {
    summary(aov(value ~ gpcr_ramp, data = .x))[[1]] %>% as.data.frame() %>% mutate(Capture = antibody, Detection = detection_ab) %>% filter(!is.na(`F value`))
  }), dunnett = map(data, ~ {
    counts <- .x %>% count(gpcr_ramp)
    
    DunnettTest(x = .x$value, g = as.factor(.x$gpcr_ramp), control = "Mock")$Mock %>%
      as.data.frame() %>% rownames_to_column("gpcr_ramp") %>%
      mutate(gpcr_ramp = str_remove(gpcr_ramp, "-Mock")) %>%
      mutate(capture = antibody, detection = detection_ab) %>%
      left_join(counts, by = "gpcr_ramp")
  }), plt_pos = map2(data, dunnett, ~ {
    # Positions of p-values in plot
    .x %>% group_by(gpcr_ramp) %>% summarise(ymax = max(value)) %>%
      left_join(.y %>% select(gpcr_ramp, pval), by = "gpcr_ramp") %>%
      filter(!is.na(pval)) %>%
      mutate(antibody = antibody, detection_ab = detection_ab,
             # Convert p-values to stars
             pval = p_to_star(pval),
             # Add some extra space (as a proportion of the range of the whole data) to have the text above the points
             # Compute in log2-scale since plotting is in log2-scale
             ypos = 2**(log2(ymax) + 0.05 * log2(diff(range(valid_clr_dat$value)))))
  }))

valid_clr_plt <- ggplot(valid_clr_dat, aes(x = gpcr_ramp, y = value)) +
  geom_hline(yintercept = 1, linetype = "dashed") +
  geom_hline(yintercept = 2, linetype = "dotted") +
  geom_beeswarm(aes(colour = detection_ab), show.legend = F) +
  geom_text(data = rbindlist(valid_clr_test$plt_pos),
            aes(y = ypos, label = pval), size = 5) +
  facet_grid2(rows = vars(detection_ab), cols = vars(antibody), axes = "all", remove_labels = T) +
  labs(x = "Interactor", y = "Signal-to-noise ratio", title = "Capture") +
  scale_colour_manual(values = c("OLLAS" = "#BFBFBF", "RAMP1" = "#BFEFFF", "RAMP2" = "#B1E063", "RAMP3" = "#EEAD0E")) +
  scale_y_continuous(trans = "log2", breaks = c(1, 4, 16, 64)) +
  theme_classic(14) +
  theme(plot.title = element_text(hjust = 0.5, size = 14))

# Extra text to the right for axis title
text_right <- ggplot(data.frame(a = "Detection", x = 1, y = 1)) +
  geom_text(aes(x = x, y = y, label = a), angle = -90, size = 5.5) +
  theme_void() +
  coord_cartesian(clip = "off")
valid_clr_plt <- valid_clr_plt + text_right + plot_layout(widths = c(22, 1))

```

```{r}
valid_clr_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_validation_CALCRL.pdf")
ggsave(valid_clr_name, valid_clr_plt, width = 7.25, height = 8.5, device = "pdf", useDingbats = F)
```

Endogenous RAMP
---------------

Figure S9

```{r}
endog_ramp <- valid_dat$data_list$mfi %>%
  select(samp_name, contains("RAMP")) %>%
  # Add sample information
  left_join(valid_dat$data_list$well_info %>%
              select(samp_name, exclude, cell_type, gpcr, ramp, detection_ab), by = "samp_name") %>%
  # Look at untransfected cells vs buffer, RAMP capture with RAMP detection
  filter(is.na(exclude), !cell_type %in% c("HUVEC"), ramp %in% c("untransfected", "empty"), detection_ab != "OLLAS") %>%
  mutate(cell_type = case_when(cell_type == "buffer" ~ "Buffer", T ~ cell_type)) %>%
  select(-exclude) %>%
  pivot_longer(cols = -c(samp_name, cell_type, gpcr, ramp, detection_ab), names_to = "binder", values_to = "value") %>%
  # Add antibody names
  left_join(valid_dat$data_list$prot %>%
              select(Antibody.name, Gene, gene_name_id), by = c("binder" = "gene_name_id")) %>%
  unite("gene_name_ab", Gene, Antibody.name, remove = F) %>%
  # Look at capture and detection of the same kind of RAMP
  filter(Gene == detection_ab) %>%
  # A few buffer only samples get NaN values, remove those
  filter(!is.na(value)) %>%
  # Remove some kind of trailing special space character, indistinguishable from a normal space but not detected by trimws, from the RAMP1 Ab name
  mutate(gene_name_ab = str_remove(gene_name_ab, "\\s")) %>%
  group_by(gene_name_ab) %>%
  nest() %>%
  mutate(anova = map(data, ~ {
    summary(aov(value ~ cell_type, data = .x))[[1]] %>% as.data.frame() %>% mutate(Capture = gene_name_ab) %>% filter(!is.na(`F value`))
  })) %>%
  mutate(dunnett = map(data, ~ {
    counts <- .x %>% count(cell_type)
    detection <- switch(str_extract(gene_name_ab, "RAMP\\d"),
                        "RAMP1" = "RAMP1_AF6428", "RAMP2" = "RAMP2_AF6427", "RAMP3" = "RAMP3_AF4875")
    
    DunnettTest(x = .x$value, g = as.factor(.x$cell_type), control = "Buffer")$Buffer %>%
      as.data.frame() %>% rownames_to_column("cell_type") %>%
      mutate(cell_type = str_remove(cell_type, "-Buffer")) %>%
      left_join(counts, by = "cell_type") %>%
      mutate(capture = gene_name_ab, detection = detection)
  })) %>%
  mutate(plt = map2(data, dunnett, ~ {
    plt_out <- ggplot(.x, aes(x = cell_type, y = value)) +
      geom_hline(yintercept = 1, linetype = "dashed") +
      geom_hline(yintercept = 1.5, linetype = "dotted") +
      geom_beeswarm() +
      scale_fill_manual(values = c("empty" = "grey", "untransfected" = "black")) +
      labs(x = NULL, y = NULL, title = gene_name_ab) +
      theme_classic(14) +
      theme(plot.title = element_text(hjust = 0.5, size = 12),
            axis.text.x = element_text(angle = 45, hjust = 1, vjust = 1))
    
    # Positions of p-values
    p_pos <- .x %>% group_by(cell_type) %>% summarise(max_y = max(value)) %>%
      right_join(.y %>% select(cell_type, pval), by = "cell_type") %>%
      mutate(y_pos = max_y + 0.1 * diff(range(.x$value)),
             p_star = p_to_star(pval))

    # No x-axis labels if top plot (apart from RAMP3)
    if (gene_name_ab %in% c("RAMP1_HPA010654", "RAMP2_HPA064452")) {
      plt_out <- plt_out + theme(axis.text.x = element_blank())
    }
    
    # Adjust scales for some plots to be more comparable
    if (gene_name_ab %in% c("RAMP1_HPA010654", "RAMP1_AF6428", "RAMP2_AF6427")) {
      plt_out <- plt_out + ylim(0.5, 3) +
        # Adjust p-value position for adjusted scale
        geom_text(data = p_pos %>% mutate(y_pos = max_y + 0.1 * diff(range(c(0.5, 3)))), aes(x = cell_type, y = y_pos, label = p_star))
    }
    # Add p-values to plot not included in previous if statements (no if else due to overlaps)
    if (gene_name_ab %in% c("RAMP2_HPA064452", "RAMP3_AF4875")) {
      plt_out <- plt_out + geom_text(data = p_pos, aes(x = cell_type, y = y_pos, label = p_star))
    }

    return(plt_out)
  }))

# Extra text to the right for axis title
text_left <- ggplot(data.frame(a = "Signal-to-noise ratio", x = 1, y = 1)) +
  geom_text(aes(x = x, y = y, label = a), angle = 90, size = 5) +
  theme_void() +
  coord_cartesian(clip = "off")
endog_ramp_plt <-
  text_left +
  (endog_ramp$plt[[1]] / endog_ramp$plt[[2]]) +
  (endog_ramp$plt[[3]] / endog_ramp$plt[[4]]) +
  (endog_ramp$plt[[5]] + plot_spacer() + plot_layout(heights = c(1.3, 1))) +
  plot_layout(widths = c(1, 9, 9, 9))
```

```{r}
endog_ramp_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_endog_ramp.pdf")
ggsave(endog_ramp_name, endog_ramp_plt, width = 7.25, height = 5, device = "pdf", useDingbats = F)
```

MolBoolean statistical analysis
===============================

Perform Anova and Dunnett test for the MolBoolean results

```{r}
molbol <- list(
  "supl10a" = read_excel("molboolean.xlsx", sheet = "Figure S10A", n_max = 9),
  "main4b" = read_excel("molboolean.xlsx", sheet = "Fig 4B", n_max = 9)
) %>%
  map(., ~ {
    # Make long format data
    mb_long <- .x %>% mutate(across(everything(), as.numeric)) %>% rownames_to_column("rn") %>%
      pivot_longer(cols = -rn) %>% filter(!is.na(value))
    
    # Statistical tests (Anova, Dunnett test)
    ap <- summary(aov(value ~ name, data = mb_long))[[1]] %>% as.data.frame() %>% slice(1)
    dp <- DunnettTest(x = mb_long$value, g = as.factor(mb_long$name),
                      control = ifelse(any(str_detect(mb_long$name, "overlap")),
                      "overlap CALCRL+RAMP1", "CALCRL+RAMP2"))[[1]] %>%
      as.data.frame() %>% rownames_to_column("rn") %>% mutate(rn = str_remove_all(rn, "overlap *")) %>%
      separate(col = rn, into = c("comparison", "control"), sep = "-") %>%
      # Add sample sizes
      left_join(count(mb_long, name) %>% mutate(name = str_remove_all(name, "overlap *")),
                by = c("comparison" = "name"))
    
    return(list("anova" = ap, "dunnett" = dp))
  })

```


P-values table
==============

```{r}
# Load p-values from expression analysis (from a different script)
cell_expr_p <- read_csv("fig_s12_pval.csv", show_col_types = F) %>%
  select(ramp = which_ramp, p.value = p_value, statistic)

# Compile p-values from tests into one table, with sheets named after which figure panel they are relevant to
pval_tbl <- list(
  "explanation" = data.frame(
    "sheet" = c("...anova", "...dunnett", "...wilcoxon", "...fisher"),
    "explanation" = c("Anova test results from the aov() and summary() functions. Contain the capture method (Capture, not for the MolBoolean assays, fig.4 and S10), degrees of freedom (Df), sums (Sum Sq) and means (Mean Sq) of squares, the test statistic (F value), and P-value (Pr(>F)).",
                      "Dunnett test results from the DunnettTest() function, testing samples (called interactor, gpcr_interactor, or comparison) against controls. Contain the capture and detection methods (capture, detection, if relevant), the number of samples of the sample type being tested (n), the difference in observed means (diff), the 95% confidence interval (lwr.ci, upr.ci), and the P-value (pval).",
                      "Wilcoxon rank-sum test results using the wilcox.test() function. Contains the comparison (gpcr, ramp), the capture method if applicable (capture), the P-value (p.value), and the test statistic (statistic).",
                      "Fisher test p-values (p.value) from the fisher.test function, comparing G protein and beta arrestin couplings between interacting and non-interacting GPCRs.")
  ),
  "fig.4B.anova" = molbol$main4b$anova %>% remove_rownames(),
  "fig.4B.dunnett" = molbol$main4b$dunnett %>% relocate(comparison, control, n),
  "fig.S3.wilcoxon" = pilot_box_p %>% rename(capture = binder) %>% mutate(panel = case_when(gpcr == "GPRC5A" ~ "A", gpcr == "HCRTR2" ~ "B"), .before = 1) %>% arrange(panel),
  "fig.S4A.anova" = ramp_expr_anova_p %>% relocate(Capture),
  "fig.S4A.dunnett" = ramp_expr_dunnett_p %>% relocate(interactor, capture, n),
  "fig.S4B.anova" = posctrl2_anova %>% relocate(Capture),
  "fig.S4B.dunnett" = posctrl2_dunnett %>% relocate(gpcr_interactor, capture, detection, n),
  "fig.S4C.anova" = posctrl1_anova %>% relocate(Capture),
  "fig.S4C.dunnett" = posctrl1_dunnett %>% relocate(gpcr_interactor, capture, detection, n),
  "fig.S8.anova" = valid_clr_test$anova %>% rbindlist() %>% relocate(Capture, Detection),
  "fig.S8.dunnett" = valid_clr_test$dunnett %>% rbindlist() %>% rename(gpcr_interactor = gpcr_ramp) %>% relocate(gpcr_interactor, capture, detection, n),
  "fig.S9.anova" = endog_ramp$anova %>% rbindlist() %>% relocate(Capture),
  "fig.S9.dunnett" = endog_ramp$dunnett %>% rbindlist() %>% relocate(cell_type, capture, detection, n),
  "fig.S10A.anova" = molbol$supl10a$anova %>% remove_rownames(),
  "fig.S10A.dunnett" = molbol$supl10a$dunnett %>% relocate(comparison, control, n),
  "fig.S12A.wilcoxon" = cell_expr_p,
  "fig.S13.fisher" = data.frame(
    "panel" = c("A", "A", "B", "C"),
    "comparison" = c("Primary", "Secondary", "", ""),
    "p.value" = c(gprot_plt$p %>% filter(value == "Primary") %>% pull(p),
                  gprot_plt$p %>% filter(value == "Secondary") %>% pull(p),
                  gprot_prim$p$p,
                  arr_plt$p$p)
  )
)
```

```{r}
pval_tbl_name <- paste0(out_dir, format(Sys.time(),"%Y-%m-%d_%H%M%S"), "_pval_tbl.xlsx")
write.xlsx(pval_tbl, pval_tbl_name, asTable = T, tableStyle = "TableStyleLight1")
```


Session information
===================

```{r session information}
sessionInfo()
```
